The ChEMBL database as Linked Open Data

### 2013-03-06 article.tex
Added a technical discussion section, answering the reviewer's question about RDF syntax errors and performance

The ongoing ChEMBL-RDF project is Open Source making it possible to others to convert ChEMBL to RDF too.
The ChEMBL team (JO, AG, MD) plans to be a primary source of a RDF version of ChEMBL, while others continue
exposing ChEMBL as RDF too (EW, PA). Various version may arise, exposing the data in different ontologies,
supporting current community needs, however, convergence is expected after a period of experimenting with ontologies that
may not prove to be practically useful. The availability of Open Source scripts ensures that the community can contribute to the
process of choosing a practically useful set of ontological terms.

>>>>

The ongoing ChEMBL-RDF project is Open Source making it possible to others to convert ChEMBL to RDF too.
Technically, the choice of PHP makes it easy to share functionality between the
here described conversion scripts, and PHP-enabled web services, used to provide the Linked
Data interface to the ChEMBL-RDF data, as is fast enough for practical uses. These scripts do
not use a library for handling RDF data. While using such libraries increases the dependencies
for the scripts, they also ensure the generation of syntactically correct RDF triples. Continued
development of the ChEMBL-RDF scripts, however, has started using RDF libraries for this purpose
specificaly for triple generation of compound names, removing code in the scripts to escape
special characters, like double quotes.

Finally, the ChEMBL team (JO, AG, MD) plans to be a primary source of a RDF version of ChEMBL, while others continue
exposing ChEMBL as RDF too (EW, PA). Various version may arise, exposing the data in different ontologies,
supporting current community needs, however, convergence is expected after a period of experimenting with ontologies that
may not prove to be practically useful. The availability of Open Source scripts ensures that the community can contribute to the
process of choosing a practically useful set of ontological terms.
